Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.

### 2020-08-22 tex/reply-to-referees.tex

\replytitle
\subsection*{Reply to Editor}
\refreplyheading

\changes
\subsection*{Reply to Comments}
\begin{itemize}

\item   \textit{``I particularly like your mapping of your estimating equation to the SIR model. But, it would be nice to discuss further the assumptions in light of the SIR model. For example, how do the orthogonality assumptions in (1) relate to the assumptions on top of page (14)? and just to be clear, you have a "causal model" yet for identification you rely on projections in the random effects specification (and no exclusion restriction). For example, what do you rule out vis a vis "diff in diff" type event study models with fixed effects? How about a brief discussion of the "invariance assumption" and why you think it would hold in your counterfactual exercise. ''}

The testable restrictions of the model are now described better.  Please see the discussion around TR. The SIR model
for example implies that testing rate is a confounder for case growth rate, but the causal model implies  that testing rate
does not affect the behavior or policy variables (other than through cases). This is an overidentification restriction.
To show the power of this approach, we also looked at imposition of other "contextual information": for example, mask
having only direct effect on growth rates (and not via behavior) or business closure policies affecting case growth rates
only through behavhior.

The fixed effect estimates lump state-level confounders in one unobservable component.  Our approach does not preclude
the use of fixed effects to estimate the model. We present fixed effects as part of Sensitivity analysis.

The invariance assumption is similar to standard assumptions in Structural VAR literature, starting with Sims (1972).

@@

We chose information structure that is parsimonious and yet, we believe, captures the  information that is most relevant for people's behavior.

Conditioning on current policy variables that is included in all specifications, the lagged values of policies will  likely add little additional information and, therefore, we decided to exclude lagged values of policies from the information structure. We may re-interpret that the coefficient of current policy variables partially reflects its effect of providing information.

On the other hand, the lagged values of  behaviors may be a part of the information structure. As a sensitivity check, we estimated a specification that includes  lagged behavior variables as information variables in Section 5.  As shown in specification (5) of Figures xx-xx, the estimated coefficients of mask for employees, closed K-12 schools, stay-at-home orders, and the average of stay-at-home orders and closures of movie theaters, restaurants, and non-essential businesses are not so sensitive to an inclusion of lagged behavior variables as information.

\item[3.]  \textit{(Expectation and Lucas critique) ``Related to the previous comment, what would be the link
between the current paper's setup and how expectations are formed given the information
structure? For example, is this paper safe from Lucas critique? Some comments would be
helpful.''}

@@

Thank you for your comment. Following your comment, we added the following sentence:
\begin{quote}
The  lagged values of behavior variable may be also included in the information set, but we postpone this discussion after the main empirical results are presented.
\end{quote} 
As a part of sensitivity checks, we now examine if the estimates are sensitive when we include two weeks lagged value of behavior variables in the information set, under which policies depend on past behavior. We find that the estimated coefficients of masks for employees are not sensitive to an inclusion of past behavior variables.

We think it is reasonable to assume that people's behavior today will not immediately affect today's policy because it takes time for policy makers to gather information on people's behavior and make a policy decision based on gathered information, especially in the early pandemic period.

\item[5.]  \textit{(Details about confidence intervals) ``Starting from Figure 1, confidence intervals are shown
in the shaded region. It is not clearly stated in the paper how they are obtained. On page 32,
in Figure 9, the authors state:
We set initial $\Delta\log\Delta C$ and $\log\Delta C$  to their values first observed in the state we
are simulating. We hold all other regressors at their observed values. Error terms
are drawn with replacement from the residuals. We do this many times and report
the average over draws of the residuals. The shaded region is a point-wise 90\%
confidence interval. It is still unclear how a pointwise confidence interval is obtained. Does this mean that a pointwise
90\% confidence interval is constructed by simulation or bootstrap? It would be useful if the authors describe how to construct a confidence interval and provide a remark why it is valid.''}

We have the following paragraph:
\begin{quote}
 To compute the estimated and counterfactual
paths, we use the   estimate   in
column ``Average'' of Table \ref{tab:dieff-si}. We set initial
$\Delta \log \Delta C$ and $\log \Delta C$ to their values first
observed in the state we are simulating. We now provide
more details on how counterfactuals are constructed -- see Section 2.
The shaded region is a point-wise 90\% confidence
interval.
\end{quote}

@@

\item[6.]  \textit{(Replication files) ``It would be great if the authors could post their dataset and replication
files on public domain such as a GitHub page or ICPSR at https://www.openicpsr.org/
openicpsr/covid19.''}

All programs and dataset will be available at our GitHub page, which is currently set to be private but we will plan to make it publicly accessible once the final version of the paper is accepted.

@@

\item[8.]  \textit{(Random effects vs. fixed effects) ``In addition to the previous comment, another reason for
preferring the random effects model could be that there could be substantial measurement
errors in behavior and policy variables. Fixed effects estimators could suffer more from measurement
errors.''}

Following your suggestion, we have added a comment on this on page xx in Section 4.2.

\item[9.]  \textit{(Multiple testing) ``There are lots of hypotheses and stars in Tables 3-7. Perhaps it might be
useful to consider multiple testing corrections by controlling the familywise error rate or a
related concept.''}

We are not doing any hypothesis testing in this paper: we are constructing point and interval predictions for 2-3 key policies. This
is in line with with IHME institute is doing (our analysis on masks predates theirs, as we posted our findings
at the end of May, and they announced their findings in middle of July). The 
"stars" are reported as a matter of statistical convention, but we never use them in any formal way.

Furthermore, we believe that testing "no mask effect" hypothesis is actually not an interesting exercise for policy analysis
or actual policy decisions.   From a decision-theoretic point of view the cost of accepting the false null is extremely high,
which could result in huge losses. The Neyman-Pearson test with $\alpha=$ small, corresponds to the idea that the cost
of the null is small (little harm done if the "no mask effect" is falsely accepted), e.g. Amemiya "Introduction to Statistics and Econometrics".  So doing "no mask effect" testing with very low $\alpha$ would correspond to assuming that the cost of deciding that masks are not effective is very low.  Multiple hypothesis testing would further drive $\alpha$ to smaller values, and we are not sure how this would align with the decision-theoretic framework.

%Remark. Elaborating further on decision-theoretic point, with $H_0$ masks being useless, the policy makers problem is to make a decision 
%to achieve minimal loss:
%$$
%\min (E [Loss (NoMask) | H_0] P[H_0], E [Loss (Mask) | H_A] P[H_A]).
%$$
%The optimal decision is not to use Masks if $$P[H_0]> \alpha = P[H_A] \cdot E [Loss (Mask) | H_A] /E [Loss (NoMask) | H_0] ),$$
%which gives the relevant $\alpha$. E.g, using $\alpha =.1$ results from the information that $P[H_A]=1/2$ and assuming that the loss from using masks has to be 5 times higher than the loss from not using masks.

 For masks, given the decision-theoretic framework, given prior evidence from RCT on efficacy of masks for respiratory deceases, (unfortunately not including corona), the interesting nulls would be "mask effects  have -.15, -.1, -.05" effects on growth rate. This null would not be  rejected no matter what adjustments to p-values we make or what sensitivity analysis we make.  Moreover, after doing all of the sensitivity exercises, we would not be able to reject this null.   This corresponds to the idea that the null hypothesis
 here is the one that is very costly if falsely rejected.

@@

\item[1.]  \textit{(Figure 1) ``What are black and grey dotted lines? It would be helpful if the authors add notes
to the figure. The same questions apply to Figures 2 and 3 and other figures.''}

Black and grey dots represent each state's change in growth rate over time.  Given that it may be difficult to digest a counterfactual change in case/death growth in introduction, we decided to focus on relative effect of policies in Figures 1-3.

\item[2.]  \textit{(Figure 4) ``What do S. \& P. stand for in Figure 4?''}

It stands for 
P. Wright and S. Wright as discussed in the footnote 2:
\begin{quote}
The father and son,
P. Wright and S. Wright closely collaborated to develop structural equation models and causal path diagrams; P. Wright's
key work represented supply-demand system as a directed acyclical graph and established its identification using
exclusion restrictions on instrumental variables.
\end{quote}

@@

\item[3.]  \textit{(Footnote 17) ``Is this necessary? This seems obvious. The authors could simply drop this
footnote or make it more informative.''}

Following your suggestion, we have dropped this footnote.

\item[4.]  \textit{(Footnote 19) ``On page 17, in footnote 19, the authors state:
We drop ``Residential' because it is highly correlated with both ``Workplace'' and
``Retail \& recreation" at correlation coefficients of 0.98.
This sentence is ambiguous. Do the authors mean that both correlation coefficients are identically 0.98? Please rephrase this sentence.''}

### 2020-08-26 tex/covidEffectOfNPI-revision.tex
update

We present a conceptual framework that spells out the causal structure on how the Covid-19 spread  is dynamically determined by policies and human behavior. Our approach explicitly recognizes that policies not only directly affect the spread of Covid-19 (e.g., mask requirement) but also indirectly affect its spread by changing people's behavior (e.g., stay-at-home order). It also recognizes that people react to new information on Covid-19 cases and deaths, and voluntarily adjust their behavior (e.g., voluntary social distancing and hand washing) even without any policy in place.  Our casual model provides a framework to quantitatively decompose the growth of Covid-19 cases and deaths into three components: (1) direct policy effect, (2) policy effect through behavior, and (3) direct behavior effect in response to new information.\footnote{The causal model is framed using the language of structural equations models and causal diagrams of econometrics (\cite{pwright, haavelmo1944, tinbergen1940, wold1954} and genetics \citep{wright1923}, with natural unfolding potential/structiral outcomes representation \citep{rubin1974,tinbergen1930,neyman:PO,imbens_rubin_2015}. See \cite{pearl:biometrika},\cite{pearl:robins},  \cite{pearl:causality}, \cite{white:chalak}, \cite{peters2020book}, \cite{heckman:pinto}, and \cite{hernanrobins2020book}  for modern developments, in computer
science, econometrics, and epidemiology. The particular causal diagram has several ``mediation" components, where variables affect outcomes directly and indirectly through other variables called mediators; these structures go back at least to \cite[][see Figure 6]{wright1923}; see, e.g., \cite{baron1986} and \cite{Hines2020} for modern treatments. The father and son, P. Wright and S. Wright closely collaborated to develop structural equation models and causal path diagrams; P. Wright's key work represented supply-demand system as a directed acyclical graph and established its identification using exclusion restrictions on instrumental variables.}
%The causal model is framed using the language of structural equations models and causal diagrams of econometrics (\cite{pwright, haavelmo1944, heckman2007}. See \cite{pearl:robins}, \cite{peters2020book}, and \cite{hernanrobins2020book} for  modern developments, especially in computer science and epidemiology), with natural unfolding potential outcomes representation \citep{rubin1974,tinbergen1930,neyman:PO,imbens_rubin_2015}. As such it naturally converses in all languages for causal inference.

@@

 \cite{pei2020} use county-level observations of reported infections and deaths in conjunction with mobility  data from SafeGraph to estimate how effective reproductive numbers in major metropolitan areas change over time. They conduct simulation of implementing all policies 1-2 weeks earlier and found that it would have resulted in reducing the number of cases and deaths by more than half. However, their study does not  explicitly analyze how policies are related to
the effective reproduction numbers. % Our study  analyzes how policies  affects the reproduction numbers through their impact on people's behavior.

@@

Whether wearing  masks in public place should be mandatory or not has been one of the most contested policy issues with health authorities of different countries providing contradiction recommendations. Reviewing evidence, \cite{Greenhalghm2020}  recognize that there is no randomized controlled trial evidence for the effectiveness of face masks,  but they state ``indirect evidence exists to support the argument for the public wearing masks in the Covid-19 pandemic."\footnote{The virus remains viable in the air for several hours, for which surgical masks may be effective. Also, a substantial fraction of individual who are infected become infectious before showing symptom onset.}
\cite{howard2020} also review available medical evidence and conclude that ``mask wearing reduces the transmissibility per contact by reducing transmission of infected droplets in both laboratory and clinical contexts.''  The laboratory findings in \cite{hou2020} suggest that the nasal cavity may be the initial site of infection followed by aspiration to the lung, supporting the argument  ``for the widespread use of masks to prevent aersol, large droplet, and/or mechanical exposure to the nasal passages.''

Given the lack of experimental evidence on the effect of masks, conducting observational studies  is useful and important. To the best of our knowledge, our paper is the first  empirical study that shows the effectiveness of  mask mandates on reducing the spread of Covid-19 by analyzing the US state-level data. This finding corroborates and is complementary to the medical observational evidence in \cite{howard2020}. Analyzing mitigation measures in New York, Wuhan, and Italy, \cite{zhangr2020} conclude that mandatory face coverings substantially reduced infections. \cite{abaluck2020}  find that the growth rates of cases and of deaths in countries with pre-existing norms that sick people should wear masks are lower by 8 to 10\% than those rates in countries with no pre-existing mask norms. Our finding
is also corroborated by a completely different causal methodology based on synthetic control 
using German data in \cite{Mitze2020}.\footnote{Our study was first released in ArXiv on May 28, 2020 whereas
 \cite{Mitze2020} was released at SSRN on June 8, 2020.}

@@

The other policy coefficients are less sensitive to the inclusion of
national case/death variables. After school closures, business closure policies has the next largest effect followed by stay-at-home
orders.  The effect of masks for employees is  
small. 
%The comparison of effects across policies should be interpreted
%with caution.  Differences between policy effects are often
%statistically insignificant; except for masks for employees, the
%policies are highly correlated and it is difficult to separate their
%effects.

@@

\afterpage{
\begin{table}[!h]
  \caption{\label{tab:dieff-con-si}Direct and Indirect Policy Effects
    without national case/death variables, \textbf{constraints imposed}}
\begin{minipage}{\linewidth}
  \centering
    \scriptsize
  \begin{tabular}{c}
    \textbf{Cases}
    \\
    \input{tables_and_figures/dieff-cases-constrain-SI}
    \\
    \textbf{Deaths}
    \\
    \input{tables_and_figures/dieff-deaths-deathsinfo-constrain-SI}
  \end{tabular}
  \smallskip
  \begin{flushleft}
    {\tiny Direct effects capture the effect of policy on case
      growth holding behavior, information, and confounders
      constant. Direct effects are given by ${\pcolor \pi}$ in
      equation (\ref{eq:R1}). Indirect effects capture how policy
      changes behavior and behavior shift case growth. They are given
      by ${\bcolor \alpha}$ from (\ref{eq:R1}) times ${\pcolor \beta}$
      from (\ref{eq:R2}). The total effect is
      ${\pcolor \pi} + {\pcolor \beta} {\bcolor \alpha}$. Column
      ``PI$\to$Y Coefficients'' shows the coefficient estimates from
      \ref{eq:R4}. Columns ``Difference''    are  the differences between
      the estimates from (\ref{eq:R4}) and the combination of
      (\ref{eq:R1}) and (\ref{eq:R2}) while column ``Average'' are their averages.
      Standard errors are computed by
      bootstrap and clustered on state.}
    %  \ref{tab:PtoY}.
    \end{flushleft}
  \end{minipage}
\end{table}
}

%
%
%\afterpage{
%\begin{table}
%  \caption{\label{tab:dieff}Direct and Indirect Policy Effects with national case/death variables}
%\begin{minipage}{\linewidth}
%  \centering
%    \scriptsize
%  \begin{tabular}{c}
%    \textbf{Cases}
%    \\
%    \input{tables_and_figures/dieff-cases-NI}
%    \\ \\
%    \textbf{Deaths}
%    \\
%    \input{tables_and_figures/dieff-deaths-deathsinfo-NI}
%    \\
%  \end{tabular}
%  \smallskip
%  \begin{flushleft}
%      \scriptsize Direct effects capture the effect of policy on case
%      growth holding behavior, information, and confounders
%      constant. Direct effects are given by ${\pcolor \pi}$ in
%      equation (\ref{eq:R1}). Indirect effects capture how policy
%      changes behavior and behavior shift case growth. They are given
%      by ${\bcolor \alpha}$ from (\ref{eq:R1}) times ${\pcolor \beta}$
%      from (\ref{eq:R2}). The total effect is
%      ${\pcolor \pi} + {\pcolor \beta} {\bcolor \alpha}$. Column
%      ``PI$\to$Y Coefficients'' shows the coefficient estimates from
%      \ref{eq:R4}. Columns ``Difference''    are  the differences between
%      the estimates from (\ref{eq:R4}) and the combination of
%      (\ref{eq:R1}) and (\ref{eq:R2}) while column ``Average'' are their averages.
%      Standard errors are computed by
%      bootstrap and clustered on state.
%    %  \ref{tab:PtoY}.
%    \end{flushleft}
%  \end{minipage}
%\end{table}
%\clearpage}
%
%
%\afterpage{
%\begin{table}
%  \caption{\label{tab:dieff}Direct and Indirect Policy Effects with national case/death variables, \textbf{Constraints imposed}}
%\begin{minipage}{\linewidth}
%  \centering
%    \scriptsize
%  \begin{tabular}{c}
%    \textbf{Cases}
%    \\
%    \input{tables_and_figures/dieff-cases-constrain-NI}
%    \\ \\
%    \textbf{Deaths}
%    \\
%    \input{tables_and_figures/dieff-deaths-deathsinfo-constrain-NI}
%    \\
%  \end{tabular}
%  \smallskip
%  \begin{flushleft}
%      \scriptsize Direct effects capture the effect of policy on case
%      growth holding behavior, information, and confounders
%      constant. Direct effects are given by ${\pcolor \pi}$ in
%      equation (\ref{eq:R1}). Indirect effects capture how policy
%      changes behavior and behavior shift case growth. They are given
%      by ${\bcolor \alpha}$ from (\ref{eq:R1}) times ${\pcolor \beta}$
%      from (\ref{eq:R2}). The total effect is
%      ${\pcolor \pi} + {\pcolor \beta} {\bcolor \alpha}$. Column
%      ``PI$\to$Y Coefficients'' shows the coefficient estimates from
%      \ref{eq:R4}. Columns ``Difference''    are  the differences between
%      the estimates from (\ref{eq:R4}) and the combination of
%      (\ref{eq:R1}) and (\ref{eq:R2}) while column ``Average'' are their averages.
%      Standard errors are computed by
%      bootstrap and clustered on state.
%    %  \ref{tab:PtoY}.
%    \end{flushleft}
%  \end{minipage}
%\end{table}
%\clearpage}

@@

Similarly to Table  \ref{tab:dieff-si}, the first three columns of  Table \ref{tab:dieff-con-si} report  the estimated direct and indirect effects of policy but imposing that masks for employees only affect cases/deaths directly without affecting behavior and that business closure policies only affects cases/deaths indirectly through its effect on behavior.\footnote{These are computed from estimating the specification in columns (1)-(4) of
Table \ref{tab:PItoB} and column (1) of Table \ref{tab:BPItoY} but imposing that the coefficient of masks for employees is zero in (\ref{eq:R1}) and that the coefficient of business closure policies is zero in (\ref{eq:R2}).} The estimated total effect of masks for employees in the third column of Table \ref{tab:dieff-con-si} is higher than that of Table  \ref{tab:dieff-si}. Similarly, the total effect of business closure policies is estimated larger in Table \ref{tab:dieff-con-si} than in  Table  \ref{tab:dieff-si}.

>>>>

We present a conceptual framework that spells out the causal structure on how the Covid-19 spread is dynamically determined by policies and human behavior. Our approach explicitly recognizes that policies not only directly affect the spread of Covid-19 (e.g., mask requirement) but also indirectly affect its spread by changing people's behavior (e.g., stay-at-home order). It also recognizes that people react to new information on Covid-19 cases and deaths, and voluntarily adjust their behavior (e.g., voluntary social distancing and hand washing) even without any policy in place. Our casual model provides a framework to quantitatively decompose the growth of Covid-19 cases and deaths into three components: (1) direct policy effect, (2) policy effect through behavior, and (3) direct behavior effect in response to new information. \footnote{The causal model is framed using the language of structural equations models and causal diagrams of econometrics (\cite{pwright, haavelmo:1944, tinbergen:1940, wold:1954, pearl:biometrika, heckman:pinto} and genetics \citep{wright1923}, with natural unfolding potential/structiral outcomes representation \citep{rubin1974,tinbergen1930,neyman:PO,imbens_rubin_2015}. See, e.g., \cite{pearl:biometrika},\cite{pearl:robins}, \cite{pearl:causality}, \cite{pearl:why}, \cite{white:chalak}, \cite{peters2020book}, \cite{heckman:pinto}, and \cite{hernanrobins2020book} for modern developments, in computer science, econometrics, and epidemiology. The particular causal diagram has several ``mediation" components, where variables affect outcomes directly and indirectly through other variables called mediators; these structures go back at least to \cite[][see Figure 6]{wright1923}; see, e.g., \cite{baron1986},\cite{Hines2020}, \cite{richardson:mediation} for modern treatments. The father and son, P. Wright and S. Wright closely collaborated to develop structural equation models and causal path diagrams; P. Wright's key work represented supply-demand system as a directed acyclical graph and established its identification using exclusion restrictions on instrumental variables.}

%We present a conceptual framework that spells out the causal structure on how the Covid-19 spread  is dynamically determined by policies and human behavior. Our approach explicitly recognizes that policies not only directly affect the spread of Covid-19 (e.g., mask requirement) but also indirectly affect its spread by changing people's behavior (e.g., stay-at-home order). It also recognizes that people react to new information on Covid-19 cases and deaths, and voluntarily adjust their behavior (e.g., voluntary social distancing and hand washing) even without any policy in place.  Our casual model provides a framework to quantitatively decompose the growth of Covid-19 cases and deaths into three components: (1) direct policy effect, (2) policy effect through behavior, and (3) direct behavior effect in response to new information.\footnote{The causal model is framed using the language of structural equations models and causal diagrams of econometrics (\cite{pwright, haavelmo1944, tinbergen1940, wold1954} and genetics \citep{wright1923}, with natural unfolding potential/structiral outcomes representation \citep{rubin1974,tinbergen1930,neyman:PO,imbens_rubin_2015}. See \cite{pearl:biometrika},\cite{pearl:robins},  \cite{pearl:causality}, \cite{white:chalak}, \cite{peters2020book}, \cite{heckman:pinto}, and \cite{hernanrobins2020book}  for modern developments, in computer
%science, econometrics, and epidemiology. The particular causal diagram has several ``mediation" components, where variables affect outcomes directly and indirectly through other variables called mediators; these structures go back at least to \cite[][see Figure 6]{wright1923}; see, e.g., \cite{baron1986} and \cite{Hines2020} for modern treatments. The father and son, P. Wright and S. Wright closely collaborated to develop structural equation models and causal path diagrams; P. Wright's key work represented supply-demand system as a directed acyclical graph and established its identification using exclusion restrictions on instrumental variables.}
%The causal model is framed using the language of structural equations models and causal diagrams of econometrics (\cite{pwright, haavelmo1944, heckman2007}. See \cite{pearl:robins}, \cite{peters2020book}, and \cite{hernanrobins2020book} for  modern developments, especially in computer science and epidemiology), with natural unfolding potential outcomes representation \citep{rubin1974,tinbergen1930,neyman:PO,imbens_rubin_2015}. As such it naturally converses in all languages for causal inference.

@@

 \cite{pei2020} use county-level observations of reported infections and deaths in conjunction with mobility  data from SafeGraph to conduct simulation of implementing all policies 1-2 weeks earlier and found that it would have resulted in reducing the number of cases and deaths by more than half. However, their study does not  explicitly analyze how policies are related to the effective reproduction numbers. % Our study  analyzes how policies  affects the reproduction numbers through their impact on people's behavior.

@@

Whether wearing  masks in public place should be mandatory or not has been one of the most contested policy issues with health authorities of different countries providing contradiction recommendations. Reviewing evidence, \cite{Greenhalghm2020}  recognize that there is no randomized controlled trial evidence for the effectiveness of face masks,  but they state ``indirect evidence exists to support the argument for the public wearing masks in the Covid-19 pandemic."\footnote{The virus remains viable in the air for several hours, for which surgical masks may be effective. Also, a substantial fraction of individual who are infected become infectious before showing symptom onset.}
\cite{howard2020} also review available medical evidence and conclude that ``mask wearing reduces the transmissibility per contact by reducing transmission of infected droplets in both laboratory and clinical contexts.''  The laboratory findings in \cite{hou2020} suggest that the nasal cavity may be the initial site of infection followed by aspiration to the lung, supporting the argument  ``for the widespread use of masks to prevent aersol, large droplet, and/or mechanical exposure to the nasal passages.''   \cite{He2020} examined temporal patterns of viral shedding in COVID-19 patients and found the highest viral load at the time of symptom onset; this suggests that a significant portion of transmission may have occurred before symptom onset and that universal face masks may be an effective control measure to reduce transmission.\footnote{\cite{Lee2020} find evidence that viral loads in asymptomatic patients are similar to those in symptomatic patients. Aerosol transmission of viruses may occur through aerosols particles released during breathing and speaking by asymptomatic infected individuals; masks reduce such airborne transmission \citep{Prather2020}. \cite{Anfinrud2020} provide visual evidence of speech-generated droplet as well as the effectiveness of cloth masks to reduce the emission of droplets.   \cite{Chu2020} conduct a meta-analysis of observational studies on transmission of the viruses that cause COVID-19 and related diseases and find the effectiveness of mask use for reducing transmission. } \cite{ollila2020} provide a meta-analyhsis of randomized controlled trials of non-surgical face masks in preventing viral respiratory infections in non-hospital and non-household settings, finding that face masks decreased infections across all five studies they reviewed.\footnote{Whether wearing masks creates a false sense of security and leads to decrease in social distancing is also a hotly debated topic.  A randomized field experiment in Berlin, Germany, conducted by \cite{seres2020}  finds that wearing masks actually increases social distancing, providing no evidence that mandatory masks leads to decrease in social distancing.}

Given the lack of experimental evidence on the effect of masks in the context of COVID-19, conducting observational studies  is useful and important. To the best of our knowledge, our paper is the first  empirical study that shows the effectiveness of  mask mandates on reducing the spread of Covid-19 by analyzing the US state-level data. This finding corroborates and is complementary to the medical observational evidence in \cite{howard2020}. Analyzing mitigation measures in New York, Wuhan, and Italy, \cite{zhangr2020} conclude that mandatory face coverings substantially reduced infections. \cite{abaluck2020}  find that the growth rates of cases and of deaths in countries with pre-existing norms that sick people should wear masks are lower by 8 to 10\% than those rates in countries with no pre-existing mask norms.\footnote{\cite{miyazawa2020} find that  country's COVID-19 death rates are negatively associated with mask wearing rates.} Our finding is also corroborated by a completely different causal methodology based on synthetic control 
using German data in \cite{Mitze2020}.\footnote{Our study was first released in ArXiv on May 28, 2020 whereas
 \cite{Mitze2020} was released at SSRN on June 8, 2020.}

@@

The other policy coefficients are less sensitive to the inclusion of
national case/death variables. After school closures, business closure policies has the next largest effect followed by stay-at-home
orders.  The effect of masks for employees is  
small.\footnote{Similar to our finding, \cite{kovacs2020} find no evidence that introduction of compulsory face mask policies affect community mobility in Germany.}

%The comparison of effects across policies should be interpreted
%with caution.  Differences between policy effects are often
%statistically insignificant; except for masks for employees, the
%policies are highly correlated and it is difficult to separate their
%effects.

@@

\afterpage{
\begin{table}[!h]
  \caption{\label{tab:dieff-con-si}Direct and Indirect Policy Effects
    without national case/death variables, \textbf{restrictions imposed}}
\begin{minipage}{\linewidth}
  \centering
    \scriptsize
  \begin{tabular}{c}
    \textbf{Cases}
    \\
    \input{tables_and_figures/dieff-cases-constrain-SI}
    \\
    \textbf{Deaths}
    \\
    \input{tables_and_figures/dieff-deaths-deathsinfo-constrain-SI}
  \end{tabular}
  \smallskip
  \begin{flushleft}
    {\tiny Direct effects capture the effect of policy on case
      growth holding behavior, information, and confounders
      constant. Direct effects are given by ${\pcolor \pi}$ in
      equation (\ref{eq:R1}). Indirect effects capture how policy
      changes behavior and behavior shift case growth. They are given
      by ${\bcolor \alpha}$ from (\ref{eq:R1}) times ${\pcolor \beta}$
      from (\ref{eq:R2}). The total effect is
      ${\pcolor \pi} + {\pcolor \beta} {\bcolor \alpha}$. Column
      ``PI$\to$Y Coefficients'' shows the coefficient estimates from
      \ref{eq:R4}. Columns ``Difference''    are  the differences between
      the estimates from (\ref{eq:R4}) and the combination of
      (\ref{eq:R1}) and (\ref{eq:R2}) while column ``Average'' are their averages.
      Standard errors are computed by
      bootstrap and clustered on state.}
    %  \ref{tab:PtoY}.
    \end{flushleft}
  \end{minipage}
\end{table}
}

\afterpage{
\begin{table}
  \caption{\label{tab:dieff-con}Direct and Indirect Policy Effects with national case/death variables, \textbf{restrictions imposed}}
\begin{minipage}{\linewidth}
  \centering
    \scriptsize
  \begin{tabular}{c}
    \textbf{Cases}
    \\
    \input{tables_and_figures/dieff-cases-constrain-NI}
    \\ \\
    \textbf{Deaths}
    \\
    \input{tables_and_figures/dieff-deaths-deathsinfo-constrain-NI}
    \\
  \end{tabular}
  \smallskip
  \begin{flushleft}
      \scriptsize Direct effects capture the effect of policy on case
      growth holding behavior, information, and confounders
      constant. Direct effects are given by ${\pcolor \pi}$ in
      equation (\ref{eq:R1}). Indirect effects capture how policy
      changes behavior and behavior shift case growth. They are given
      by ${\bcolor \alpha}$ from (\ref{eq:R1}) times ${\pcolor \beta}$
      from (\ref{eq:R2}). The total effect is
      ${\pcolor \pi} + {\pcolor \beta} {\bcolor \alpha}$. Column
      ``PI$\to$Y Coefficients'' shows the coefficient estimates from
      \ref{eq:R4}. Columns ``Difference''    are  the differences between
      the estimates from (\ref{eq:R4}) and the combination of
      (\ref{eq:R1}) and (\ref{eq:R2}) while column ``Average'' are their averages.
      Standard errors are computed by
      bootstrap and clustered on state.
    %  \ref{tab:PtoY}.
    \end{flushleft}
  \end{minipage}
\end{table}
\clearpage}

%
%
%\afterpage{
%\begin{table}
%  \caption{\label{tab:dieff}Direct and Indirect Policy Effects with national case/death variables}
%\begin{minipage}{\linewidth}
%  \centering
%    \scriptsize
%  \begin{tabular}{c}
%    \textbf{Cases}
%    \\
%    \input{tables_and_figures/dieff-cases-NI}
%    \\ \\
%    \textbf{Deaths}
%    \\
%    \input{tables_and_figures/dieff-deaths-deathsinfo-NI}
%    \\
%  \end{tabular}
%  \smallskip
%  \begin{flushleft}
%      \scriptsize Direct effects capture the effect of policy on case
%      growth holding behavior, information, and confounders
%      constant. Direct effects are given by ${\pcolor \pi}$ in
%      equation (\ref{eq:R1}). Indirect effects capture how policy
%      changes behavior and behavior shift case growth. They are given
%      by ${\bcolor \alpha}$ from (\ref{eq:R1}) times ${\pcolor \beta}$
%      from (\ref{eq:R2}). The total effect is
%      ${\pcolor \pi} + {\pcolor \beta} {\bcolor \alpha}$. Column
%      ``PI$\to$Y Coefficients'' shows the coefficient estimates from
%      \ref{eq:R4}. Columns ``Difference''    are  the differences between
%      the estimates from (\ref{eq:R4}) and the combination of
%      (\ref{eq:R1}) and (\ref{eq:R2}) while column ``Average'' are their averages.
%      Standard errors are computed by
%      bootstrap and clustered on state.
%    %  \ref{tab:PtoY}.
%    \end{flushleft}
%  \end{minipage}
%\end{table}
%\clearpage}
%
%
%\afterpage{
%\begin{table}
%  \caption{\label{tab:dieff}Direct and Indirect Policy Effects with national case/death variables, \textbf{restrictions imposed}}
%\begin{minipage}{\linewidth}
%  \centering
%    \scriptsize
%  \begin{tabular}{c}
%    \textbf{Cases}
%    \\
%    \input{tables_and_figures/dieff-cases-constrain-NI}
%    \\ \\
%    \textbf{Deaths}
%    \\
%    \input{tables_and_figures/dieff-deaths-deathsinfo-constrain-NI}
%    \\
%  \end{tabular}
%  \smallskip
%  \begin{flushleft}
%      \scriptsize Direct effects capture the effect of policy on case
%      growth holding behavior, information, and confounders
%      constant. Direct effects are given by ${\pcolor \pi}$ in
%      equation (\ref{eq:R1}). Indirect effects capture how policy
%      changes behavior and behavior shift case growth. They are given
%      by ${\bcolor \alpha}$ from (\ref{eq:R1}) times ${\pcolor \beta}$
%      from (\ref{eq:R2}). The total effect is
%      ${\pcolor \pi} + {\pcolor \beta} {\bcolor \alpha}$. Column
%      ``PI$\to$Y Coefficients'' shows the coefficient estimates from
%      \ref{eq:R4}. Columns ``Difference''    are  the differences between
%      the estimates from (\ref{eq:R4}) and the combination of
%      (\ref{eq:R1}) and (\ref{eq:R2}) while column ``Average'' are their averages.
%      Standard errors are computed by
%      bootstrap and clustered on state.
%    %  \ref{tab:PtoY}.
%    \end{flushleft}
%  \end{minipage}
%\end{table}
%\clearpage}

@@

Similarly to Table  \ref{tab:dieff-si}, the first three columns of  Table \ref{tab:dieff-con-si} report  the estimated direct and indirect effects of policy but imposing that masks for employees only affect cases/deaths directly without affecting behavior and that business closure policies only affect  cases/deaths indirectly through their effects on behavior.\footnote{These are computed from estimating the specification in columns (1)-(4) of
Table \ref{tab:PItoB} and column (1) of Table \ref{tab:BPItoY} but imposing that the coefficient of masks for employees is zero in (\ref{eq:R1}) and that the coefficient of business closure policies is zero in (\ref{eq:R2}).} The estimated total effect of masks for employees in the third column of Table \ref{tab:dieff-con-si} is higher than that of Table  \ref{tab:dieff-si}. Similarly, the total effect of business closure policies is estimated larger in Table \ref{tab:dieff-con-si} than in  Table  \ref{tab:dieff-si}.

Column ``Difference''  in Tables   \ref{tab:dieff-si} and \ref{tab:dieff-con-si}  show the
difference between the estimate of (\ref{eq:R4}) in column  ``PI$\to$Y Coefficient''   and the implied estimate from
(\ref{eq:R1})-(\ref{eq:R2}) in   column ``Total.''   Differences  are generally small except for the coefficient of closed K-12 schools and  the sum of all policies in Table   \ref{tab:dieff-si}. The large differences in school closures  may be due to the  difficulty in identifying the effect of school closures given a lack of cross-sectional variations. Imposing the coefficients of masks for employees and business closure policies to be zero in (\ref{eq:R1}) and  (\ref{eq:R2}), respectively, does not increase differences between  ``Total" and  ``PI$\to$Y Coefficient''  as reported in the last column of  Table \ref{tab:dieff-con-si}.

 Tables  \ref{tab:dieff} and \ref{tab:dieff-con}  present the results for a specification that includes national information variables, where the estimates on masks for employees are similar to those in  Tables  \ref{tab:dieff-si} and \ref{tab:dieff-con-si}. Column ``Difference''  of Table \ref{tab:dieff-con} indicates that the restrictions of zero coefficients for masks for employees in (\ref{eq:R1}) and for business closure policies in  (\ref{eq:R2}) are not statistically rejected.
